Detecting Hate Speech with GPT-3

### 2021-03-23 outputs/documents/paper.Rmd
Fix a typo identified while uploading

```{r comparison, fig.cap="Comparing accurancy with and without an instruction", fig.height = 3}
few_shot_mixed_result <- read.csv(here::here("outputs/data/few_shot_fixed_examples_results.csv"))

>>>>

```{r comparison, fig.cap="Comparing accuracy with and without an instruction", fig.height = 3}
few_shot_mixed_result <- read.csv(here::here("outputs/data/few_shot_fixed_examples_results.csv"))
